Transmembrane helices are an overlooked and evolutionarily conserved source of major histocompatibility complex class I and II epitopes

### 2021-12-12 frontiers.tex
Have figure 1 and 2

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=10cm]{logo1}% This is a *.eps file
\end{center}
\caption{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures}\label{fig:1}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=15cm]{logos}
\end{center}
\caption{This is a figure with sub figures, \textbf{(A)} is one logo, \textbf{(B)} is a different logo.}\label{fig:2}
\end{figure}

>>>>

% Added by RJCB
% Subfigures
%\usepackage{subcaption} % Already added

% Added by RJCB
% Subfigure numbers use uppercase, 
% from https://tex.stackexchange.com/a/278140
\renewcommand{\thesubfigure}{\Alph{subfigure}}

% Added by RJCB
\usepackage{listings}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{verbatim}
\usepackage{pgf}
\usepackage{bm}
\usepackage{multirow}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{booktabs}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\usepackage{longtable}

@@

%
% Figure 1
%
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.8\textwidth]{bbbq_article_figures_Page_1}% This is a *.eps file
\end{center}
\caption{
    \textbf{Over-presentation of TMH-derived epitopes on most MHC-I and -II alleles}
    \textbf{(A)} 
    The percentage of epitopes for MHC-I and -II alleles that are predicted to 
    overlap with TMHs for the proteomes of SARS-CoV-2 (top row), human (middle 
    row) and \emph{M. tuberculosis} (MtB; bottom row).
    The pair of horizontal red lines in each plot indicate the lower and upper bound 
    of the 99\% confidence interval.
    See supplementary Tables \ref{tab:tmh_binders_mhc2} and \ref{tab:tmh_binders_mhc1}
    for the exact TMH and  epitope counts.
    \textbf{(B-C)}
    Correlation between the percentages of predicted TMH-derived epitopes
    and the hydrophobicity score of all predicted epitopes for 
    human MHC-I \textbf{(B)} and MHC-II alleles \textbf{(C)}.
    Diagonal red line: linear regression analysis. 
    Labels are shorthand for the HLA alleles,
    see the supplementary Table \ref{tab:haplotype_abbreviations} for the names.}
  \label{fig:1}
\end{figure}
% 1A: \label{fig:bbbq_1_smart_results}
% 1B: \label{fig:hydrophobicity_1}
% 1C: \label{fig:hydrophobicity_2}

%
% Figure 2
%
\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{bbbq_article_figures_Page_2}% This is a *.eps file
\end{center}
\caption{
    \textbf{
      Analysis of epitope database shows that TMH derived epitopes are over presented.
    }
    The percentage of epitopes for MHC-I and -II alleles that overlap with TMHs
    that are presented. The pair of horizontal red lines in each plot indicate the
    lower and upper bound of the 99\% confidence interval. Note that only one line
    is visible as this interval is relatively narrow. 
    Alleles are listed in Table \ref{tab:haplotype_abbreviations}).
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes for MHC-I alleles. 
    \textbf{(B)} 
    MHC ligands from IEDB corresponding to TMH-derived epitopes. 
    The numbers above the bars denotes the number of TMH derived epitopes obtained.
}
\label{fig:elution}
\end{figure}
% Figure 2a: \label{fig:2a}
% Figure 2b: \label{fig:2b}
